How to Analyze Build Logs

### 2021-04-16 tse-paper/rebuttal.tex

\documentclass[10pt,a4wide]{article}
\usepackage[paper=a4paper,margin=0.85in]{geometry}
\usepackage{relsize}
\usepackage{paralist} % so that compactitems and enumerations can be made more compact
\usepackage{graphicx}
\usepackage{url}
\usepackage{booktabs}
\usepackage{boxedminipage}
\usepackage{wasysym}
\usepackage{framed}
\usepackage{etoolbox}
\usepackage{xcolor}

\definecolor{todo}{HTML}{00a3cc}
\newcommand{\todo}[1] {{\bfseries \color{todo} #1}}
\newcommand{\caro}[1] {\todo{[Caro: #1]} }

@@

\vspace{-1cm}

\begin{tabular}{|lp{11cm}|}
\hline
%\textbf{Manuscript number} & \\
\textbf{Original Title} & 
How to Analyze Build Logs: A Systematic Survey and Comparative Study of Chunk Retrieval Techniques \\
\textbf{Authors} & Carolin Brandt, Moritz Beller\\
\textbf{Corresponding author} & Carolin Brandt (c.e.brandt@tudelft.nl)\\
\textbf{Revision date} & TODO \\ %\date October 1st, 2020\\
\textbf{Journal} & IEEE Software \\
\hline
\end{tabular}
\vspace{1cm}

\noindent
Dear Editor,\\
Dear Reviewers,
\\\\
\noindent

We submitted a previous version of this manuscript to the ``Transactions on Software Engineering'' journal,
which \todo{resulted in a ``revise and resubmit" verdict''}
Based on the feedback from the reviewers, we revised the manuscript 
\todo{describe key points, like improving the structure to make our intentions clearer and make the paper easier to follow for readers}
We decided to submit this paper to the Empirical Software Engineering Journal,
as we believe that a core part of our paper---the empirical evaluation of the
chunk retrieval techniques---fit the scope of this journal better.
We thank the original reviewers for their in-depth and constructive feedback
which enabled us to improve and sharpen our work.

\noindent
Below we outline the remarks from the original reviews and our response
in e-mail quotation and answer style.

% We thank reviewers for their in-depth and constructive feedback. All reviewers are
% positive about the relevance of the paper for IEEE Software’s
% readership (assessing it Very Relevant or Relevant). Reviewer 2 calls it a “great paper” and
% Reviewer 1 “clearly written and easy to read,” “highly relevant and
% fits well for IEEE Software and its target audience.” Reviewer 3,
% while being perhaps most critical overall, notes that “[the paper]
% focuses on a much needed dual perspective integrating the developer’s
% own perception to measure productivity. The paper is very well
% motivated and overall easy to read.”

% That said, there were a number of points that needed to be changed in the paper, in particular as regards scope and structure. We have made several improvements to
% the paper following your recommendations for this major revision.  Key changes include:
% \begin{itemize}
% \item Re-structuring the manuscript, by putting visualizations into a side bar to make the article focused on the productivity study alone.
%   \item Adding further details on study methodology and execution to the Telemetry and Regression Model sections while keeping the spirit of a light-weight, practitioner-oriented paper. In particular, we made the section on regression models easier to read for readers without a statistics background. 
% \item Fixing the detailed remarks by the reviewers (throughout the paper).
% \end{itemize}

% \noindent
% Below we outline the remarks from the reviewers and our response in e-mail quotation and 
% answer style.

%\noindent
Best regards,
\\
Carolin Brandt and Moritz Beller
\\\\
\noindent

### 2021-04-16 tse-paper/paper.tex
fix some feedback + literature authors missing + overhanging table

@@

@@

\title{How to Analyze Build Logs%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}
}
\subtitle{A~Systematic Survey and Comparative Study of Chunk~Retrieval~Techniques}

@@

\begin{abstract}
Build logs are the textual by-products that automatic software build processes
create, often as part of their Continuous Integration (CI)
pipeline.
Build logs can serve as a paramount source of
information for developers to understand and debug dependency, compilation, or
test failures.
Manually
extracting the important chunks of information in a build log, though, is akin to
finding a needle in a haystack.
Recently, practitioners and researchers have started attempts to partly
automate
this time-consuming activity, to not only ease
developers' debugging task but also to enable a novel class of
automated onward processing applications.
In this paper, we give a systematic overview of the emerging field of build log analysis.
In a broad literature mapping survey, we first survey and categorize the existing methods to
extract information chunks from build logs.
In the second part of the paper, we then develop prototypical implementations of three promising
techniques to analyze build logs, namely program synthesis
by example, textual similarity, and keyword search.
Finally, we evaluate the techniques in an empirical study on
almost 800 build logs 
from a wide range of different projects and programming languages.
Our findings show that none of the three techniques in general outperforms
the others, but rather, that each technique has its respective strengths
and weaknesses.
We discuss under which circumstances each technique performs best
and provide a recommendation scheme for when developers or researchers might 
use which technique.
We close with a roadmap of important open problems in the field of
build log analysis.
\keywords{Continuous Integration \and Build Log Analysis \and Chunk Retrieval}
\end{abstract}

@@

When a build or one of its steps fails, developers typically scavenge
the logs for information related to the source of the error.
This
manual activity is tedious and prone to
errors~\citep{santolucito2018statically}.
As a single build log can be
over 50 megabytes large~\citep{beller2017oops}, finding the small chunk
of information linked to the actual error, is akin to
searching for a needle in a haystack.
The large number of unrelated, but ambiguous
warnings which many build
logs regularly contain further compounds this problem.
In addition to helping
understand and fix build failures, the information richness of build
logs enables a plethora of other applications: with the help of build
logs, we can better understand and categorize CI failures and compile
errors~\citep{islam2017insights,seo2014programmers}, differentiate
testing practices~\citep{orellana2017differences,vassallo2017a-tale},
train classifiers to do ``predictive CI'' on the build or test outcome
and
duration~\citep{ni2017cost,bisong2017built,haghighatkhah2018test,
machalica2019predictive},
or investigate the role of automated static analysis tools (ASATs)
in CI
builds~\citep{zampetti2017open}.

@@

Retrospectively analyzing the build logs is not the only solution to
the problem---an alternate would be to integrate live plugins into the
build process
 such as the JUnit
plugin for Jenkins~\citep{jenkins2020junit-plugin} or
Deflaker by Bell et al.~\citep{bell2018deflaker}.

Their advantage is that they can precisely report the information which
is required.
However, such plugins are not available for all build tools, they are
non-trivial to implement one-off solutions, and they
do not enable the analysis of historical builds.
When using such a plugin, one has to decide
beforehand which information should be reported, whereas
build log analysis enables us to leverage all information
present in the build logs.
Moreover, build log analysis is the more general solution.
While they serve an important niche, custom plugins do not make build
log analysis redundant.

@@

To answer this question, we start the investigation in this
paper---pictured in
\Cref{fig:overview}---with an
extensive literature survey (step \circlenum{1}).
The survey identifies various strategies to
analyze build logs, among which are developing
custom parsers, using regular expressions, doing manual inspections,
searching for keywords, or performing natural language processing.

However, it also identifies that there is currently no guidance on when
to use which of these
approaches.
Unfortunately, our survey also shows that
less than half of the 61 works which rely on build log analysis
describe it in sufficient detail and that
the few available implementations are all based on either a custom parser
or regular expressions.
These two approaches are problematic, as their creation
and maintenance is manual and expensive, does not generalize across build
logs from different build tools, and is prone to errors,
as the experience of
TravisTorrent has
shown~\citep{beller2017travistorrent,travistorrentquestions}.
In fact, some even ``strongly discourage'' the creation of such
parsers~\citep{urli2018design}.
In summary, the outcome of our literature survey shows the need for a new
generation of automated techniques to analyze build logs, which are
openly available and documented in detail, together with
guidance on when to use which technique.

To fill this gap, we created three novel, prototypical implementations
to automatically analyze build logs (step \circlenum{2}) by retrieving
a substring (chunk)
from the build log.
Our
implementations are based on the most widely used approaches
from the literature survey and as such, are meant to serve as
the ``smallest common denominator,'' with as little tuning and
optimization as possible to stand prototypical for the ideas
they represent:
\begin{itemize}
	\item \emph{Programming by Example (PBE)}, a technique
	able to
	automatically synthesize regular expressions,
	\item a technique based on information
	retrieval, which we call \emph{Common Text Similarity (CTS)},
	\item inspired by the manual ad hoc search for key parts in the
	log, a
	technique employing \emph{Keyword Search (KWS)}.
\end{itemize}

@@

Due to this ambiguity, we develop a set of guidelines
on how to choose the most suitable build log analysis
technique for the task at hand (step \circlenum{4}).
We recommend PBE for use cases where the desired information is always
represented in the same structural way and high confidence in
precision and recall of the chunk retrieval is required.
The results PBE produces are suited for automatic onward processing.
CTS is
well-suited when the representation of the desired information varies
slightly and the output of the chunk retrieval is further processed by
a human.
In cases where the textual representation of the desired
information in the log is unpredictable or varies greatly, KWS seems
to be the best choice.
However, its low precision---it extracts a
context of multiple lines around a found keyword---makes it generally
unsuited for automatic onward processing.
Instead, KWS requires a human
to further inspect and interpret the output chunk.
A hybrid solution combining the three techniques might be the best
all-round solution.
Finally, we give a roadmap to guide future research in the field
of build log analysis.

In short, this article contributes
\begin{itemize}
\item the first systematic survey of the emerging field of build log
analysis.
\item three prototypical open-sourced implementations of
promising chunk retrieval techniques.
\item a large empirical study comparing the three techniques.
\item a documented replication package~\citep{brandt2020chunk-replication}.
\end{itemize}

\begin{figure}[tb]
	\centering
	\includegraphics[width=0.7\columnwidth, clip]{img/lit_survey_svg2.pdf}
	\caption{Literature selection (following Petersen et
	al.~\citep{petersen2015guidelines}).}
	\label{fig:lit-survey}
\end{figure}

\section{Systematic Literature Mapping Survey}
\label{sec:survey}
% tense: past

In this section, we report on the state-of-research in the emerging
field of build log analysis by means of a systematic mapping study.
We start with a differentiation of build log analysis
from the older field of
system log analysis.
% ref to fig 2 so it can be here and above fig 3
Then, we describe the methodology (\Cref{fig:lit-survey})
and results of our systematic mapping
survey following the
guidelines by Petersen et
al.~\citep{petersen2008systematic,petersen2015guidelines}.
% We close by summarizing how build logs are commonly
% analyzed in literature and discuss the implications of these findings.

@@

Some of the techniques developed to parse system logs can operate
on build logs as well, such as approaches to retrieve the
values of variable parts in a log message, e.g.\, by using regular
expressions~\citep{nagappan2010abstracting,xu2009detecting}.
% This is the easiest example matching here
% amar et al are not in our literature survey
However, the number of
system logs generated mandates that scalability and efficiency play a
much more important role than for build logs.
In addition, almost all of the techniques developed to analyze system logs
leverage their inherent event structure.
Build logs generally lack this
structure and thus require different bespoke approaches.

@@

The first step in a systematic literature survey is to
establish which works one wants to cover and how to find
them~\citep{kitchenham2009systematic}.
Since the field of build log analysis is relatively young, we
surveyed as broad a population of scientific material as possible.
We did not limit the sources to specific Software Engineering
venues~\citep{petersen2015guidelines}, but included all sources
monitored by Google Scholar, including Bachelor's theses, Master's
theses, and academic slide decks.
We use Google Scholar as opposed to Scopus or
other databases because it is the search engine for scholarly material
with
the broadest and most current index, including preprints.

\Cref{fig:lit-survey} gives an overview of the literature selection
process.
An initial Google Scholar search for ``build log''
returned more than 2.2 million results on the 15th of March 2020, many
of which stem
from unrelated fields such as construction or wood working.
We refined the search criteria to exclude such obvious
non-related fields and to exclude works on system
logs (see \Cref{sec:system-log-analysis}).
This left us with 1,552 search results.
% Our replication package documents the full search
% queries~\citep{brandt2020chunk-replication}.
To make handling so many search results feasible, we employed a
three-pass filtering strategy:

@@

@@

To support the data extraction we created a template which we filled out
for each of the 61 works.
The template contained questions to answer RQ 1.1 through RQ 1.3,
for example ``Is the technique explained in detail?'' and
``What is the source of the build logs?''
As recommended by Petersen et
al.~\citep{petersen2015guidelines}, we started the mapping survey with a
pilot:
both authors extracted data from the same five works and held a
consensus meeting to unify their understanding
of the data extraction template.
We divided the remaining 56 works evenly between the two authors
and inspected each work as closely as necessary to fill out the
template
with confidence,
starting from occurrences of ``log'' or ``build'' within the full
text of the work.

@@

In this section, we first give a general overview over our paper
population.
We then present the results of the analysis phase along RQs 1.1 through
1.3.

\subsubsection{Descriptive Study Statistics}
\begin{figure}[tbp]
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/lit-sur/years.pdf}
		\caption{Number of works analyzing build logs per year.}
		\label{fig:lit-years}
\end{figure}

After the third filtering phase, we finally included 61 works in the
literature survey.
The majority of these are scientific articles (81\%), of which all but
three have been peer-reviewed and published (94\%).
The remaining works are theses (14\%), two books, and one slide deck.

@@

In this section, we describe what sort of information the works in
our survey usually retrieve from build logs.
\Cref{fig:litsur_r} depicts these results.

@@

@@

\addtolength{\tabcolsep}{-5pt}
\begin{table*}[tbhp]
\tinyish
\centering
\caption{Overview of build log analysis techniques.}
\begin{tabularx}{\textwidth}{@{}lXl@{}}

\raisebox{0.8mm}{Parser} &
\raisebox{0.8mm}{
\citep{vassallo2018un-break,zhang2016android,seo2014programmers,hassan2019tackling,hassan2017automatic,chromy2007integration,mesbah2019deepdelta,wen2018blimp,kwon2018prioritizing,adams2007design,rahman2018impact,brandyberry2006continuous,tomassi2019bugswarm,ren2018automated,vassallo2019automated,cavalcanti2019impact,sippola2013qt,felipe2012towards,shi2018evaluating,urli2018design,selberg2012use}
} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_21.pdf}
\\

\raisebox{0.8mm}{Regular expression} &
\raisebox{0.8mm}{
\citep{beller2017oops,hassan2017change,macho2018automatically,vassallo2017a-tale,lou2019history,hassan2017automatic,rott2019empirische,zampetti2019study,zhao2018comparing,rausch2017empirical,ghaleb2019studying,zampetti2017open,zhang2019large,kavaler2019tool,morris2010experience}
} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_15.pdf}
\\

\raisebox{0.8mm}{Manual inspection} &
\raisebox{0.8mm}{
\citep{sulir2016quantitative,hassan2017automatic,bouabana2019theory,barinov2017applying,silva2018build,ghaleb2019empirical,marcozzi2019systematic,hukkanen2015adopting,rausch2017empirical,hassan2017mining,zolfagharinia2017not,cassee2019impact}
} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_12.pdf}
\\

\raisebox{0.8mm}{Machine Learning} &
\raisebox{0.8mm}{
\citep{hassan2017change,lou2019history,lindqvist2019detection,ren2018automated,schulz2017active}
} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_5.pdf}
\\

\raisebox{0.8mm}{Natural Language Processing}	&
\raisebox{0.8mm}{
\citep{hassan2017change,lou2019history,schulz2017active}
} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\

\raisebox{0.8mm}{Information Retrieval} &
\raisebox{0.8mm}{
\citep{hassan2017change,lindqvist2019detection,ren2018automated}
} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\

\raisebox{0.8mm}{Analysis} &
\raisebox{0.8mm}{
\citep{sulir2016quantitative,haghighatkhah2018test,durieux2019critical}
} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\

\raisebox{0.8mm}{Keyword Search} &
\raisebox{0.8mm}{
\citep{brandyberry2006continuous,zhang2019large,kavaler2019tool}
} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\

\raisebox{0.8mm}{Scan} &
\raisebox{0.8mm}{
\citep{clemencic2014new,hibbard2001visualization}
} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_2.pdf}
\\

\raisebox{0.8mm}{Other} &
\raisebox{0.8mm}{
\citep{zhang2016android,hassan2017change,lou2019history,silva2018build,ren2018automated,schulz2017active}
} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_10.pdf}
\\

\raisebox{0.8mm}{None identified} &
\raisebox{0.8mm}{
\citep{macho2017preventing,felipe2012towards,orellana2017differences,madeyski2017continuous,zhao2017impact,santolucito2018statically,makihara2018multi,mcintosh2012evolution,gallaba2018noise,matthies2016scrumlint}
} &
\\

\end{tabularx}
\label{tab:litsur:techniques}
\end{table*}
\addtolength{\tabcolsep}{5pt}

@@

Only 25\% of the works claimed their implementation is available.
Moreover, we
saw some reuse of the few available build log analysis tools.
Five works employed the tools used to create
\emph{TravisTorrent}~\citep{beller2017oops,
orellana2017differences,zhao2018comparing} or
an updated version of them~\citep{rott2019empirische,
shi2018evaluating}, two used the
\emph{Maven Log Analyzer}~\citep{macho2018automatically,gallaba2018noise},
and
another two
\emph{MAKAO}~\citep{wen2018blimp,adams2007design}.

\subsubsection{Which kinds of build logs are subject to
  analysis (RQ 1.3)?}
As the structure of build logs can change greatly depending on which
build tools output to it~\citep{staahl2014modeling},
we were interested in which build tools are
investigated in the literature.
\Cref{fig:litsur:log_producer} shows the distribution of
build tools whose logs were analyzed by the works in our survey.
Of the works, 30\% analyzed
Maven~\citep{maven2019website},
16\% analyzed Gradle~\citep{gradle2020website},
and 10\% analyzed Ant build logs~\citep{ant2020website}.

@@

In 38\% of cases, the works collected build logs from Travis
CI~\citep{travisci2019webpage};
18\% of the works analyzed logs from TravisTorrent; and 8\% included
build logs from industrial projects.
The number of logs analyzed varied greatly between the works
and we were not always able to
extract it confidently.
23 of the works analyzed more than a thousand build logs, while one
investigated up to 122 million logs.
Of the surveyed works, 31\% claim to have published their data to
enable further research.
However, we found no clear reuse of build log data sets with the
exception of TravisTorrent~\citep{beller2017travistorrent}, which
Vassallo et al.~\citep{vassallo2017a-tale},
Ghaleb et al.~\citep{ghaleb2019studying},
and several others have studied~\citep{hassan2017change,
hassan2019tackling,hassan2017automatic,orellana2017differences,
haghighatkhah2018test,madeyski2017continuous,ghaleb2019empirical,
santolucito2018statically,gallaba2018noise,shi2018evaluating}.

>>>>

\usepackage{pdflscape}

@@

\definecolor{todo}{HTML}{00a3cc}
% \newcommand{\todo}[1] {{\bfseries \color{todo} #1}}
% \newcommand{\caro}[1] {\todo{[Caro: #1]} } 
% hide todos:
\newcommand{\todo}[1] {}
\newcommand{\caro}[1] {}

@@

\title{How to Analyze Build Logs%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}
}
\subtitle{A~Systematic Mapping and Comparative Study of Chunk~Retrieval~Techniques}

@@

\begin{abstract}
Build logs are the textual by-products that automatic software build processes
create, often as part of their Continuous Integration (CI)
pipeline.
Build logs can serve as a paramount source of
information for developers to understand and debug dependency, compilation, or
test failures.
Manually
extracting the important chunks of information in a build log, though, is akin to
finding a needle in a haystack.
Recently, practitioners and researchers have started attempts to partly
automate
this time-consuming activity, to not only ease
developers' debugging task but also to enable a novel class of
automated onward processing applications.
In this paper, we give a systematic overview of the emerging field of build log analysis.
In a broad literature mapping, we first survey and categorize the described methods to
extract information chunks from build logs.
In the second part of the paper, we then develop prototypical implementations of three promising
techniques to analyze build logs, namely program synthesis
by example, textual similarity, and keyword search.
Finally, we evaluate the techniques in an empirical study on
almost 800 build logs 
from a wide range of different projects and programming languages.
Our findings show that none of the three techniques in general outperforms
the others, but rather, that each technique has its respective strengths
and weaknesses.
We discuss under which circumstances each technique performs best
and provide a recommendation scheme for when developers or researchers might 
use which technique.
We close with a roadmap of important open problems in the field of
build log analysis.
\keywords{Continuous Integration \and Build Log Analysis \and Chunk Retrieval}
\end{abstract}

@@

When a build or one of its steps fails, developers typically scavenge
the logs for information related to the source of the error.
\todo{cite bart paper?}
This
manual activity is tedious and prone to
errors~\citep{santolucito2018statically}.
As a single build log can be
over 50 megabytes large~\citep{beller2017oops} \todo{check, reviewer comment}, finding the small chunk
of information linked to the actual error, is akin to
searching for a needle in a haystack.
The large number of unrelated, but ambiguous
warnings which many build
logs regularly contain further compounds this problem.
In addition to helping
understand and fix build failures, the information richness of build
logs enables a plethora of other applications: with the help of build
logs, we can better understand and categorize CI failures and compile
errors~\citep{islam2017insights,seo2014programmers}, differentiate
testing practices~\citep{orellana2017differences,vassallo2017a-tale},
train classifiers to do ``predictive CI'' on the build or test outcome
and
duration~\citep{ni2017cost,bisong2017built,haghighatkhah2018test,
machalica2019predictive},
or investigate the role of automated static analysis tools (ASATs)
in CI
builds~\citep{zampetti2017open}.

@@

Retrospectively analyzing the build logs is not the only solution to
the problem---an alternate would be to integrate live plugins into the
build process such as the JUnit
plugin for Jenkins\footnote{https://plugins.jenkins.io/junit/} or
Deflaker~\citep{bell2018deflaker}.

Their advantage is that they can precisely report the information which
is required.
However, such plugins are not available for all build tools, they are
non-trivial to implement, and
do not enable the analysis of historical builds.
When using such a plugin, one has to decide
beforehand which information should be reported, whereas
build log analysis enables us to leverage all information
present in the build logs.
Moreover, build log analysis is the more general solution.
While custom plugins serve an important niche, they do not make build
log analysis redundant.

@@

To answer this question, we start the investigation in this
paper---pictured in
\Cref{fig:overview}---with an
extensive literature mapping (step \circlenum{1}).
Researchers describe various strategies to
analyze build logs, among which are developing
custom parsers, using regular expressions, doing manual inspections,
searching for keywords, or performing natural language processing.

However, the mapping identifies that there is currently no guidance on when
to use which of these approaches.
Unfortunately, it also shows that
less than half of the 61 works which rely on build log analysis
describe it in sufficient detail and that
the few available implementations are all based on either a custom parser
or regular expressions.
These two approaches are problematic, as their creation
and maintenance is manual and expensive, does not generalize across build
logs from different build tools, and is prone to errors,
as the experience of TravisTorrent has
shown~\citep{beller2017travistorrent}.
In fact, some even ``strongly discourage'' the creation of such
parsers~\citep{urli2018design}.
In summary, the outcome of our literature mapping shows the need for a new
generation of automated techniques to analyze build logs, which are
openly available and documented in detail, together with
guidance on when to use which technique.

To fill this gap, we created three novel, prototypical implementations
to automatically analyze build logs (step \circlenum{2}) by retrieving
a substring (chunk) from the build log.
Our
implementations are based on widely described approaches
from the literature mapping and as such, are meant to serve as
the ``smallest common denominator,'' with as little tuning and
optimization as possible to stand prototypical for the ideas
they represent:
\begin{itemize}
	\item \emph{Programming by Example (PBE)}, a technique
	able to
	automatically synthesize regular expressions,
	\item a technique based on information
	retrieval, which we call \emph{Common Text Similarity (CTS)},
	\item inspired by the manual ad-hoc search for key parts in the
	log, a
	technique employing \emph{Keyword Search (KWS)}.
\end{itemize}

@@

Due to this ambiguity, we develop a set of guidelines
on how to choose the most suitable build log analysis
technique for the task at hand (step \circlenum{4}).
We recommend PBE for use cases where the desired information is always
represented in the same structural way and high confidence in
precision and recall of the chunk retrieval is required.
The results PBE produces are suited for automatic onward processing.
CTS is
well-suited when the representation of the desired information varies
slightly and the output of the chunk retrieval is further processed by
a human.
In cases where the textual representation of the desired
information in the log is unpredictable or varies greatly, KWS is
the best choice.
However, its low precision---it extracts a
context of multiple lines around a found keyword---makes it generally
unsuited for automatic onward processing.
Instead, KWS requires a human
to further inspect and interpret the output.
A hybrid solution combining the three techniques might be the best
all-round solution.
Finally, we give a roadmap to guide future research in the field
of build log analysis.
Our implementation, experiment and analysis are documented
in our replication package~\citep{brandt2020chunk-replication}.

In short, this article contributes
\begin{itemize}
\item the first systematic mapping of the emerging field of build log
analysis.
\item three prototypical open-sourced implementations of
promising chunk retrieval techniques.
\item a large empirical study comparing the three techniques.
\end{itemize}

\begin{figure}[tb]
	\centering
	\includegraphics[width=0.7\columnwidth, clip]{img/lit_mapping_svg2.pdf}
	\caption{Literature selection (following Petersen et
	al.~\citep{petersen2015guidelines}).}
	\label{fig:lit-mapping}
\end{figure}

\section{Systematic Literature Mapping}
\label{sec:mapping}
% tense: past

In this section, we report on our systematic mapping study of how
researchers analyze build logs.
We start with a differentiation of build log analysis
from the older field of system log analysis.
% ref to fig 2 so it can be here and above fig 3
Then, we describe the methodology (\Cref{fig:lit-mapping})
and results of our systematic mapping study following the
guidelines by Petersen et
al.~\citep{petersen2008systematic,petersen2015guidelines}.
% We close by summarizing how build logs are commonly
% analyzed in literature and discuss the implications of these findings.

@@

Some of the techniques developed to parse system logs can operate
on build logs as well, such as approaches to retrieve the
values of variable parts in a log message, e.g.\, by using regular
expressions~\citep{nagappan2010abstracting,xu2009detecting}.
% This is the easiest example matching here
% amar et al are not in our literature mapping
However, the number of
system logs generated mandates that scalability and efficiency play a
much more important role than for build logs.
In addition, almost all of the techniques developed to analyze system logs
leverage their inherent event structure.
Build logs generally lack this
structure and thus require different bespoke approaches.

@@

The first step in a systematic literature mapping is to
establish which works one wants to cover and how to find
them~\citep{kitchenham2009systematic}.
Since the field of build log analysis is relatively young, we
mapped as broad a population of scientific material as possible.
We did not limit the sources to specific Software Engineering
venues~\citep{petersen2015guidelines}, but included all sources
monitored by Google Scholar, including Bachelor's theses, Master's
theses, and academic slide decks.
We use Google Scholar as opposed to Scopus or
other databases because it is the search engine for scholarly material
with
the broadest and most current index, including preprints.

\Cref{fig:lit-mapping} gives an overview of the literature selection
process.
An initial Google Scholar search for ``build log''
returned more than 2.2 million results on the 15th of March 2020, many
of which stem
from unrelated fields such as construction or wood working.
We refined the search criteria to exclude such obvious
non-related fields and to exclude works on system
logs (see \Cref{sec:system-log-analysis}).
This left us with 1,552 search results.
% Our replication package documents the full search
% queries~\citep{brandt2020chunk-replication}.
To make handling so many search results feasible, we employed a
three-pass filtering strategy:

@@

\begin{figure}[tbp]
		\centering
		\includegraphics[width=0.8\textwidth,
		clip]{img/lit-sur/years.pdf}
		\caption{Number of works analyzing build logs per year.}
		\label{fig:lit-years}
\end{figure}

\paragraph{Descriptive Study Statistics}
After the third filtering phase, we finally included 61 works in the
literature mapping.
The majority of these are scientific articles (81\%), of which all but
three have been peer-reviewed and published (94\%).
The remaining works are theses (14\%), two books, and one slide deck.

@@

To support the data extraction we created a template which we filled out
for each of the 61 works.
The template contained questions to answer RQ 1.1 through RQ 1.3,
for example ``Is the technique explained in detail?'' and
``What is the source of the build logs?''
As recommended by Petersen et
al.~\citep{petersen2015guidelines}, we started the mapping with a
pilot:
both authors extracted data from the same five works and held a
consensus meeting to unify their understanding
of the data extraction template.
We divided the remaining 56 works evenly between the two authors
and inspected each work as closely as necessary to fill out the
template
with confidence,
starting from occurrences of ``log'' or ``build'' within the full
text of the work.

@@

In this section, we present the results of the analysis phase along RQs 1.1 through
1.3.
\todo{if defining the RQs went up in the last section, rephrase the rqs here too}

@@

In this section, we describe what sort of information the works in
our mapping usually retrieve from build logs.
\Cref{fig:litsur_r} depicts these results.

@@

\begin{landscape}
\addtolength{\tabcolsep}{-5pt}
\begin{table*}[tbhp]
\tinyish
\centering
\caption{Overview of build log analysis techniques.}
\begin{tabularx}{1.5\textwidth}{lXl}

{Parser} &
\citep{vassallo2018un-break} \citep{zhang2016android} \citep{seo2014programmers} \citep{hassan2019tackling} \citep{hassan2017automatic} \citep{chromy2007integration} \citep{mesbah2019deepdelta} \citep{wen2018blimp} \citep{kwon2018prioritizing} \citep{adams2007design} \citep{rahman2018impact} \citep{brandyberry2006continuous} \citep{tomassi2019bugswarm} \citep{ren2018automated} \citep{vassallo2019automated} \citep{cavalcanti2019impact} \citep{sippola2013qt} \citep{felipe2012towards} \citep{shi2018evaluating} \citep{urli2018design} \citep{selberg2012use}
 &
\includegraphics[width=0.35\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_21.pdf}
\\

{Regular expression} &
\citep{beller2017oops} \citep{hassan2017change} \citep{macho2018automatically} \citep{vassallo2017a-tale} \citep{lou2019history} \citep{hassan2017automatic} \citep{rott2019empirische} \citep{zampetti2019study} \citep{zhao2018comparing} \citep{rausch2017empirical} \citep{ghaleb2019studying} \citep{zampetti2017open} \citep{zhang2019large} \citep{kavaler2019tool} \citep{morris2010experience}
 &
\includegraphics[width=0.35\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_15.pdf}
\\

{Manual inspection} &
{
\citep{sulir2016quantitative,hassan2017automatic,bouabana2019theory,barinov2017applying,silva2018build,ghaleb2019empirical,marcozzi2019systematic,hukkanen2015adopting,rausch2017empirical,hassan2017mining,zolfagharinia2017not,cassee2019impact}
} &
\includegraphics[width=0.35\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_12.pdf}
\\

{Machine Learning} &
{
\citep{hassan2017change,lou2019history,lindqvist2019detection,ren2018automated,schulz2017active}
} &
\includegraphics[width=0.35\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_5.pdf}
\\

{Natural Language Processing}	&
{
\citep{hassan2017change,lou2019history,schulz2017active}
} &
\includegraphics[width=0.35\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\

{Information Retrieval} &
{
\citep{hassan2017change,lindqvist2019detection,ren2018automated}
} &
\includegraphics[width=0.35\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\

{Analysis} &
{
\citep{sulir2016quantitative,haghighatkhah2018test,durieux2019critical}
} &
\includegraphics[width=0.35\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\

{Keyword Search} &
{
\citep{brandyberry2006continuous,zhang2019large,kavaler2019tool}
} &
\includegraphics[width=0.35\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\

{Scan} &
{
\citep{clemencic2014new,hibbard2001visualization}
} &
\includegraphics[width=0.35\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_2.pdf}
\\

{Other} &
{
\citep{zhang2016android,hassan2017change,lou2019history,silva2018build,ren2018automated,schulz2017active}
} &
\todo{why is this not in the graph?, find bar graphic}
\\

{None identified} &
{
\citep{macho2017preventing,felipe2012towards,orellana2017differences,madeyski2017continuous,zhao2017impact,santolucito2018statically,makihara2018multi,mcintosh2012evolution,gallaba2018noise,matthies2016scrumlint}
} &
\includegraphics[width=0.35\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_10.pdf}
\\

\end{tabularx}
\label{tab:litsur:techniques}
\end{table*}
\addtolength{\tabcolsep}{5pt}
\end{landscape}

@@

@@

Only 25\% of the works stated that they make their
implementation available for reuse.
We saw some reuse of the few available build log analysis tools.
Five works employed the tools used to create
\emph{TravisTorrent}~\citep{beller2017oops,
orellana2017differences,zhao2018comparing} or
an updated version of them~\citep{rott2019empirische,
shi2018evaluating}, two used the
\emph{Maven Log Analyzer}~\citep{macho2018automatically,gallaba2018noise},
and another two
\emph{MAKAO}~\citep{wen2018blimp,adams2007design}.

\subsubsection{Which kinds of build logs are subject to
  analysis (RQ 1.3)?}
As the structure of build logs can change greatly depending on which
build tools output to it~\citep{staahl2014modeling},
we were interested in which build tools are
investigated in the literature.
\Cref{fig:litsur:log_producer} shows the distribution of
build tools whose logs were analyzed by the works in our mapping.
Of the works, 30\% analyzed
Maven\footnote{https://maven.apache.org/},
16\% analyzed Gradle\footnote{https://gradle.org/},
and 10\% analyzed Ant build logs\footnote{https://ant.apache.org/}.

@@

In 38\% of cases, the works collected build logs from Travis
CI\footnote{https://travis-ci.org};
18\% of the works analyzed logs from TravisTorrent; and 8\% included
build logs from industrial projects.
The number of logs analyzed varied greatly between the works
and we were not always able to
extract it confidently.
23 of the works analyzed more than a thousand build logs, while one
investigated up to 122 million logs.
Of the mapped works, 31\% claim to have published their data to
enable further research.
However, we found no clear reuse of build log data sets with the
exception of TravisTorrent~\citep{beller2017travistorrent}, which
Vassallo et al.~\citep{vassallo2017a-tale},
Ghaleb et al.~\citep{ghaleb2019studying},
and several others have studied~\citep{hassan2017change,
hassan2019tackling,hassan2017automatic,orellana2017differences,
haghighatkhah2018test,madeyski2017continuous,ghaleb2019empirical,
santolucito2018statically,gallaba2018noise,shi2018evaluating}.
